%% 
%% Compliance testing for biblatex style: harvard-agsm
%% 
%% See the introduction of this document for information about the document, how
%% to use it, how to modify it, and for licencing and copyright information.
%% 
\documentclass[a4paper,landscape,12pt]{article}
\usepackage[style=harvard-agsm,backend=biber,defaultpkgs]{biblatex}
\usepackage[hidelinks]{hyperref}
\usepackage[left=6em,right=6em,top=5em,bottom=8em]{geometry}
\usepackage{color,longtable}

% 
% DOCUMENT METADATA
% 
\title{The \texttt{harvard-agsm} Bibliography and Citation Styles}
\date{18 April 2017}
\author{ultimatelostcause}

% 
% BIBLIOGRAPHIES
%
\addbibresource{agsm.bib}
\addbibresource{unsw.bib}

% 
% USEFULE RESOURCES
%
% http://tex.stackexchange.com/questions/209941/placement-of-jr-and-sr-with-biblatex
% http://tex.stackexchange.com/questions/111363/exclude-fullcite-citation-from-bibliography

% 
% CONFIGURATION
% 

% Increase the space between columns.
\setlength{\columnsep}{2em}

% Increase the space between table rows.
\renewcommand{\arraystretch}{1.5}

% Set the column widths.
\newlength\q
\setlength\q{\dimexpr .47\textwidth -2\tabcolsep}
\newlength\qr
\setlength\qr{\dimexpr .06\textwidth -2\tabcolsep}

% 
% COMMANDS AND ENVIRONMENTS
%

% Citation command for generating citations as if they were full entries in the bibliography.
\DeclareCiteCommand{\fullcite}
  {\usebibmacro{prenote}}
  {\usedriver
    {}
    {\thefield{entrytype}}}
  {\multicitedelim}
  {\usebibmacro{postnote}}

% Table for citation examples and generated content, including header row.
\newenvironment{citetable}
  {\noindent\begin{longtable}{p{\q} p{\q} p{\qr}}\textbf{Expected} & \textbf{Generated} & \textbf{IDs}\\}
  {\end{longtable}}

% Commands for formating non-compliant example
\newcommand{\majorissue}[1]{\textcolor{red}{#1}}
\newcommand{\minorissue}[1]{\textcolor{blue}{#1}}
\newcommand{\trivialissue}[1]{#1 *}

% Convenience command for formatting a URL in an example.
\newcommand{\citeurlex}[1]{%
  \let\oldurlfont\UrlFont%
  \def\UrlFont{}%
  \textless\url{#1}\textgreater%
  \let\UrlFont\oldurlfont}

% 
% CONTENT
%
\begin{document}

\twocolumn[\maketitle]
\tableofcontents
\clearpage

\section{Introduction}

This document demonstrates how the \texttt{harvard-agsm} bibliography and citation styles for bib\LaTeX{} comply (or not) with the author-year referencing style as defined in the Australian Government \textit{Style Manual} (6th edn).

\subsection{Using this document}

This document compares examples of citations and bibliography entries from the Australian Government \textit{Style Manual} (6th edn), as well as other academic sources, with citations and bibliography entries generated by bib\LaTeX{} using the \texttt{harvard-agsm} style.  The document is split into separate parts per source, with the source cited at the beginning of each part.  The structure of each part reflects as closely as possible the structure of the original source.

The examples from the original source are given in the left column, and the matching generated citation or bibliography entry is given in the centre column.  If a generated entry does not match exactly the given example, depending on how substantially it differs from the source example it should be shown:

\begin{itemize}
	\item in \textbf{red} if the difference is significant (e.g. incorrect item order, missing information, etc);
	\item in \textbf{blue} if the difference is small but substantive (e.g. different spelling, substantive differences in punctuation, etc); or
	\item followed by an \textbf{asterisk} if difference is non-substantive (e.g. trivial difference in punctuation, etc).
\end{itemize}

For each source there is a separate bib\LaTeX{} bibliography (\texttt{.bib}) file containing the bibliography entries used to generate the examples.  The entries should appear in the bibliography file in the order they appear in this document, unless there is a compelling reason in the interest of testing to the contrary.  Entry IDs are a common prefix per source and the sequence number in which they appear, e.g. \texttt{agsm12} for the 12 entry corresponding to the Australian Government \textit{Style Manual} examples.  The IDs of any entries used to generate an example appear in the right column.

\subsection{Licence and copyright}

This implementation of the \texttt{harvard-agsm} style is distributed under the conditions of the LaTeX Project Public License, either version 1.3c of this licence or (at your option) any later version.  The latest version of this licence can be found at \url{http://www.latex-project.org/lppl.txt} and version 1.3c or later is part of all distributions of LaTeX version 1 May 2005 or later.

This document contains content in the form of example of citations and bibliography entries which have been reproduced from other copyrighted works.  Such content is used in this document under the fair dealing provision of the \textit{Copyright Act 1968 (Cth)} and does not constitute a claim to any rights over the content.  The original source is acknowledged at the beginning of each document part that uses the source.

\subsection{Known issues}

The \texttt{harvard-agsm} style is not compliant with the author-year referencing style as defined in the AGSM in the following ways:

\subsubsection{Major issues}

\begin{itemize}
	\item Citations do not include contribution type.
	\item Pseudo-dates ``forthcoming'' and ``in press'' not supported.
	\item A separate entry needs to be created in the bibliography file to generate stub references for short author names.
	\item Citation-only format for newspaper articles not support.
	\item Special sources not supported.
	\item Order of details in related entry incorrect.
\end{itemize}

\subsubsection{Minor issues}

\begin{itemize}
	\item Name suffix appears after family name rather than after given initials in reference list.
	\item ``vol.'' used instead of ``vols'' for volume range in reference list.
	\item Special characters in page number not supported in bibliography file entries without also specifying ``p.''.
	\item Extended date components displayed in wrong order in reference when URL specified.\footnote{The AGSM states on p.~230 that \\A document within a web site can usefully be considered in the same way as a published document or a book''.  However, the media release example contradicts this by moving the day and month before the publisher and location, which differs from the usual ordering described for media releases at p.~207, and there is no explicit mention of the need to re-order these components.}
	\item Title of mail list displayed in italics rather than quoted in normal font.
	\item Email address of mail list user wrapped in parentheses.
\end{itemize}

\subsubsection{Trivial issues}

\begin{itemize}
	\item A comma is used instead of a semi-colon to separate multiple citations of works by the same author when page numbers are given.
	\item Year range is not shown in compact format.
\end{itemize}

\clearpage
\subsection{Cite commands}

The following examples compare all supported cite commands:

\begin{description}
	\item[cite] \cite{agsm}
	\item[citeauthor] \citeauthor{agsm}
	\item[citedate] \citedate{agsm}
	\item[citetitle] \citetitle{agsm}
	\item[citeurl] \citeurl{agsm}
	\item[citeyear] \citeyear{agsm}
	\item[fnotecite] \pnotecite{agsm}
	\item[footcite] \footcite{agsm}
	\item[footcitetext] \footcitetext{agsm}
	\item[footfullcite] \footfullcite{agsm}
	\item[fullcite] \fullcite{agsm}
	\item[notecite] \notecite{agsm}
	\item[parencite] \parencite{agsm}
	\item[parenciteyear] \parenciteyear{agsm}
	\item[pnotecite] \pnotecite{agsm}
	\item[smartcite] \smartcite{agsm}
	\item[textcite] \textcite{agsm}
\end{description}

\onecolumn

\clearpage
\part{Australian Government Style Manual}
\fullcite{agsm}
\newrefsection

\section{The citation details: authorship and year}

\subsection{One author or authoring body}

\begin{citetable}
	The theory was first propounded in 1993 (Hamilton 1994). & The theory was first propounded in 1993 \parencite{agsm1}. & \texttt{agsm1} \\
	The theory was first propounded by Hamilton (1994). & The theory was first propounded by \textcite{agsm1}. & \texttt{agsm1} \\
	The initiative was proposed in 1996 (Tourism Taskforce 1996). & The initiative was proposed in 1996 \parencite{agsm2}. & \texttt{agsm2} \\
	The Tourism Taskforce (1996) proposed the initiative. & The \textcite{agsm2} proposed the initiative. & \texttt{agsm2} \\
	Hamilton, CL 1994 & \fullcite{agsm1} & \texttt{agsm1} \\
	Tourism Taskforce 1996 & \fullcite{agsm2} & \texttt{agsm2} \\
\end{citetable}

\subsection{An authoring body with a long name}

\begin{citetable}
	The National Health and Medical Research Council prepared the guidelines in 1998 and 1999 (NHMRC 1999). & The National Health and Medical Research Council prepared the guidelines in 1998 and 1999 \parencite{agsm3}. & \texttt{agsm3} \\
	NHMRC---\textit{see} National Health and Medical Research Council. & \fullcite{agsm4} & \texttt{agsm4} \\
\end{citetable}

\subsection{Two or more works cited at one point in the text}

\begin{citetable}
	(Larsen 2000; Malinowski 1999) & \parencite{agsm5, agsm6} & \texttt{agsm5} \texttt{agsm6} \\
\end{citetable}

\subsection{Two or three authors or authoring bodies}

\begin{citetable}
	(Australian Bureau of Statistics \& Australian Institute of Health and Welfare 1997) & \parencite{agsm7} & \texttt{agsm7} \\
	(Malinowski, Miller \& Gupta 1995) & \parencite{agsm8} & \texttt{agsm8} \\
	Malinowski, Miller and Gupta (1995) disagreed with & \textcite{agsm8} disagreed with & \texttt{agsm8} \\
	Australian Bureau of Statistics \& Australian Institute of Health and Welfare 1997 & \fullcite{agsm7} & \texttt{agsm7} \\
	Malinowski, W, Miller, TB \& Gupta, K 1995 & \fullcite{agsm8} & \texttt{agsm8} \\
\end{citetable}

\subsection{More than three authors or authoring bodies}

\begin{citetable}
	(Milinowski et al. 1999) & \parencite{agsm9} & \texttt{agsm9} \\
	Milinowski et al. (1999) have found & \textcite{agsm9} have found & \texttt{agsm9} \\
	Milinowski, W, Larsen, AA, Ngu, B \& Fairweather, S 1999 & See the bibliography. & \texttt{agsm9} \\
	(Melinowski, Larsen, Ngu \& Barlen 1999) & \parencite{agsm10} & \texttt{agsm10} \\
	(Melinowski, Larsen, Ngu \& Fairweather 1999) & \parencite{agsm11} & \texttt{agsm11} \\
	(Melinowski, Miller et al. 1999) & \parencite{agsm12} & \texttt{agsm12} \\
\end{citetable}

\subsection{Citing page numbers or other elements of a work}

\begin{citetable}
	The initiative was proposed in 1996 (Tourism Taskforce 1996, p. 245) & The initiative was proposed in 1996 \parencite[p.~245]{agsm2} & \texttt{agsm2} \\
	Hamilton (1994, pp.~145--7) was the first to propound the theory. & \textcite[pp.~145--7]{agsm1} was the first to propound the theory. & \texttt{agsm1} \\
	The Public Land Use Commission reported \textellipsis (1996, pp. 27--45; 1997, p. 118) & The Public Land Use Commission reported \textellipsis \parenciteyears[pp.~27--45]{agsm14}[p.~118]{agsm13} & \texttt{agsm13} \texttt{agsm14} \\
	(Public Land Use Commission 1996, vol.~2) & \parencite[vol.~2]{agsm14} & \texttt{agsm14} \\
	(Hamilton 1994, secs~2, 7) & \parencite[secs~2,~7]{agsm1} & \texttt{agsm1} \\
	(Larsen 2000, eqs 2--6) & \parencite[eqs~2--6]{agsm6} & \texttt{agsm6} \\
	(Public Land Use Commission 1996, vol.~2, p.~23) & \parencite[vol.~2, p.~23]{agsm14} & \texttt{agsm14} \\
	(Public Land Use Commission 1996, vol.~2, p.~23; vol.~3, pp.~57--69) & \trivialissue{\parencite[vol.~2, p.~23; vol.~3, pp.~57--69]{agsm14}} & \texttt{agsm14} \\
	Public Land Use Commission (1996, vol.~2, p.~23) & \textcite[vol.~2,~p.~23]{agsm14} & \texttt{agsm14} \\
	Public Land Use Commission (1996, vol.~2, p.~23; vol.~3, pp.~57--69) & \trivialissue{\textcite[vol.~2, p.~23; vol.~3, pp.~57--69]{agsm14}} & \texttt{agsm14} \\
\end{citetable}

\subsection{More than one work by the same author or authoring body}

\subsubsection{Published in different years}

\begin{citetable}
	(Public Land Use Commission 1996, 1997) & \parencite{agsm13, agsm14} & \texttt{agsm13} \texttt{agsm14} \\
	The Public Land Use Commission (1996, 1997) reported on & The \textcite{agsm13, agsm14} reported on & \texttt{agsm13} \texttt{agsm14} \\
	(Public Land Use Commission 1996, p. 237; 1997, p. 159) & \trivialissue{\parencites[p.~237]{agsm14}[p.~159]{agsm13}} & \texttt{agsm13} \texttt{agsm14} \\
\end{citetable}

\subsubsection{Published in the same year}

\begin{citetable}
	The Australian Council of Social Service \textellipsis{} (ACOSS 1997a, 1997b). & The Australian Council of Social Service \textellipsis{} \parencite{agsm15, agsm16} & \texttt{agsm15} \texttt{agsm16} \\
	(ACOSS 1997a, p.~31; 1997b, p.~72) & \trivialissue{\parencites[p.~31]{agsm15}[p.~72]{agsm16}} & \texttt{agsm15} \texttt{agsm16} \\
	(ACOSS 1997a, 1997b; Malinowski 1999) & \parencite{agsm5, agsm15, agsm16} & \texttt{agsm5} \texttt{agsm15} \texttt{agsm16} \\
	(ACOSS 1997a, p.~31; 1997b, p.~72; Malinowski 1999, pp. 89--99) & \trivialissue{\parencites[p.~31]{agsm15}[p.~72]{agsm16}[pp.~89--99]{agsm5}}& \texttt{agsm5} \texttt{agsm15} \texttt{agsm16} \\
	National Natural Resource Management Taskforce 1999a, \textit{Managing natural resources in rural Australia for a sustainable future}, discussion paper, Agriculture, Fisheries and Forestry---Australia, Canberra, March, pp. 19--41. & \fullcite{agsm18}\nocite{agsm18b} & \texttt{agsm18a} \texttt{agsm18b} \\
\end{citetable}

\subsection{Authors with the same family name}

\begin{citetable}
	The theory was first propounded in 1993 (Humilton, CL 1994), but since then many of its elements have been hotly debated (see, for example, Humilton, M 1996, pp. 157--93). & The theory was first propounded in 1993 \parencite{agsm19a}, but since then many of its elements have been hotly debated (see, for example, \cite[pp.~157--93]{agsm19b}). & \texttt{agsm19a} \texttt{agsm19b} \\
	CL Humilton (1994) first propounded the theory in 1993, but since then many of its elements have been hotly debated; notable among the critics is M Humilton (1996). & \textcite{agsm19a} first propounded the theory in 1993, but since then many of its elements have been hotly debated; notable among the critics is \textcite{agsm19b}. & \texttt{agsm19a} \texttt{agsm19b} \\
\end{citetable}

\subsection{An edited, compiled, revised or translated work}

\begin{citetable}
	(ed. Singh 1998) & \majorissue{\parencite{agsm20}} & \texttt{agsm20} \\
	edited by Singh (1998) & edited by \textcite{agsm20} & \texttt{agsm20} \\
	(trans. Holfstadter 1999) & \majorissue{\parencite{agsm21}} & \texttt{agsm21} \\
	translated by Holstadter (1999) & translated by \textcite{agsm21} & \texttt{agsm21} \\
	Holfstadter, H (trans.) 1999 & \fullcite{agsm21} & \texttt{agsm21} \\
	Singh, K (ed.) 1998 & \fullcite{agsm20} & \texttt{agsm20} \\
	Proust, M 1970, \textit{Jean Santeuil}, trans. G Hopkins & \fullcite{agsm22} & \texttt{agsm22} \\
\end{citetable}

\subsubsection{Additional non-AGSM examples demonstrating eds, comp., comps and rev.}

\begin{citetable}
	(eds Neyland, MG \& Duncan, F 1997) & \majorissue{\parencite{agsm23}} & \texttt{agsm23} \\
	(comp. Duncan, F 1999) & \majorissue{\parencite{agsm24}} & \texttt{agsm24} \\
	(comps Neyland, MG \& Duncan, F 1999) & \majorissue{\parencite{agsm25}} & \texttt{agsm25} \\
	(rev. Snooks \& Co. 2002) & \majorissue{\parencite{agsm26}} & \texttt{agsm26} \\
\end{citetable}

\subsection{Different types of reference list entries beginning with the same name}

\begin{citetable}
	Neyland, MG 1999 & \majorissue{See the bibliography.}\nocite{agsm27,agsm28,agsm29,agsm30} & \texttt{agsm27} \\
	------\& Duncan, F 1998, & & \texttt{agsm28} \\
	Neyland, MG (ed.) 1990, & & \texttt{agsm29} \\
	------\& Duncan, F (comps) 1994, & & \texttt{agsm30} \\
\end{citetable}

\subsection{A work other than a first edition}

\begin{citetable}
	(Strunk \& White 1979) & \parencite{agsm31} & \texttt{agsm31} \\
	Strunk and White (1979) & \textcite{agsm31} & \texttt{agsm31} \\
	Strunk, W Jr \& White, EB 1979, \textit{The elements of style}, 3rd edn & \minorissue{\fullcite{agsm31}} & \texttt{agsm31} \\
\end{citetable}

\subsection{Unknown or uncertain dates}

\begin{citetable}
	(Al Mahdi n.d.) & \parencite{agsm32} & \texttt{agsm32} \\
	Al Mahdi (n.d.) & \textcite{agsm32} & \texttt{agsm32} \\
	(Al Mahdi c.~1943) & \parencite{agsm33} & \texttt{agsm33} \\
	Al Mahdi (c.~1943) & \textcite{agsm33} & \texttt{agsm33} \\
	Al Mahdi, S c.~1943 & \fullcite{agsm33} & \texttt{agsm33} \\
	(Al Mahdi 1944?) & \parencite{agsm34} & \texttt{agsm34} \\
	Al Mahdi (1944?) & \textcite{agsm34} & \texttt{agsm34} \\
	Al Mahdi, S 1944? & \fullcite{agsm34} & \texttt{agsm34} \\
	(Weinberg forthcoming) & \majorissue{\parencite{agsm35}} & \texttt{agsm35} \\
	Weinberg (forthcoming) & \majorissue{\textcite{agsm35}} & \texttt{agsm35} \\
	Weinberg, MM forthcoming & \majorissue{\fullcite{agsm35}} & \texttt{agsm35} \\
	(Weinberg in press) & \majorissue{\parencite{agsm36}} & \texttt{agsm36} \\
	Weinberg (in press) & \majorissue{\textcite{agsm36}} & \texttt{agsm36} \\
	Weinberg, MM in press & \majorissue{\fullcite{agsm36}} & \texttt{agsm36} \\
\end{citetable}

\subsection{No ascertainable author or authoring body}

\begin{citetable}
	This was apparently not the case before about 1995 (\textit{The entrepreneur's guide to the law} 1999). & This was apparently not the case before about 1995 \parencite{agsm37} & \texttt{agsm37} \\
	In \textit{The entrepreneur's guide to the law} (1999) it is claimed that this was not the case before about 1995. & In \textcite{agsm37} it is claimed that this was not the case before about 1995. & \texttt{agsm37} \\
\end{citetable}

\subsection{Pseudonymous works}

\begin{citetable}
	(Saki 1915) & \parencite{agsm38} & \texttt{agsm38} \\
	Eliot (1866) & \textcite{agsm39} & \texttt{agsm39} \\
	Saki (HH Munro) 1915 & \fullcite{agsm38} & \texttt{agsm38} \\
	Eliot, George (pseud. of Mary A Evans) 1866 & \fullcite{agsm39} & \texttt{agsm39} \\
	Sand, George (pseud.) 1856 & \fullcite{agsm40} & \texttt{agsm40} \\
\end{citetable}

\subsection{Use of a short title}

\begin{citetable}
	The Feachem report (1995) recommended & The \textcite{agsm41} recommended & \texttt{agsm41} \\
	Ralph (1999) recommended & \textcite{agsm42} recommended & \texttt{agsm42} \\
	Feachem report---\textit{see} Department of Human Services and Health (1995) & See the bibliography.\nocite{agsm41,agsm41a} & \texttt{agsm41} \texttt{agsm41a} \\
	Ralph, JT 1999---\textit{see} Review of Business Taxation. & See the bibliography.\nocite{agsm42,agsm42a} & \texttt{agsm42} \texttt{agsm42a} \\
\end{citetable}

\subsection{Parts of a publication contributed by someone other than the author}

\begin{citetable}
	Maurois (in Proust 1970) claimed & Maurois (in \cite{agsm22}) claimed & \texttt{agsm22} \\
	(Maurois, in Proust 1970) & (Maurois, in \cite{agsm22}) & \texttt{agsm22} \\
	Proust, M 1970, \textit{Jean Santeuil}, trans. G Hopkins, Simon \& Schuster, New York. Preface by Andr\'{e} Maurois. & \minorissue{\fullcite{agsm22}} & \texttt{agsm22} \\
\end{citetable}

\subsection{Citations from secondary sources}

\begin{citetable}
	Ngu (cited in Larson 1991) reported & Ngu (cited in \cite{agsm44}) reported & \texttt{agsm44} \\
	(Ngu, cited in Larson 1991) & (Ngu, cited in \cite{agsm44}) & \texttt{agsm44} \\
	Larsen, S 1991 & \fullcite{agsm44} & \texttt{agsm44} \\
\end{citetable}

\subsection{Encyclopedias and dictionaries}

\begin{citetable}
	\textit{The Macquarie dictionary} (1997) defines it as & \textcite{agsm45} defines it as & \texttt{agsm45} \\
	(\textit{The Cambridge encyclopedia of the English language} 1995) & \parencite{agsm46} & \texttt{agsm46} \\
\end{citetable}

\section{Document information}

\subsection{Books}

\begin{citetable}
	Topp, L \& Dillon, P 1996, \textit{Looking to the future: a second generation of drug research}, monograph no. 29, National Drug and Alcohol Research Centre, University of New South Wales, Sydney, pp. 29--45. & \fullcite{agsm47} & \texttt{agsm47} \\
\end{citetable}

\subsubsection{Title of book}

\begin{citetable}
	Comfort, A 1997, \textit{A good age}, & \fullcite{agsm48} & \texttt{agsm48} \\
	Intellectual Property and Competition Review Committee 2000, \textit{Parallel importation: interim report}, & \fullcite{agsm49} & \texttt{agsm49} \\
	Birtwhistle, BB 1976, \textit{The annotated `Jane Eyre'}, & \fullcite{agsm50} & \texttt{agsm50} \\
	Jung, CG 1964, \textit{Der Mensch und seine Symbole} (Man and his symbols), & \fullcite{agsm51} & \texttt{agsm51} \\
	Sand, George (psued.) 1856, \textit{The story of my life} (in French), & \fullcite{agsm40} & \texttt{agsm40} \\
\end{citetable}

\subsubsection{Title of series}

\begin{citetable}
	Wilson, C 1984, \textit{England's apprenticeship 1603--1763}, Social and economic history of England, & \fullcite{agsm52} & \texttt{agsm52} \\
	Wilson, C 1985, \textit{England's apprenticeship 1603--1763}, Social and economic history of England, 2nd edn, ed. Asa Briggs, & \fullcite{agsm53} & \texttt{agsm53} \\
\end{citetable}

\subsubsection{Description of work}

\begin{citetable}
	Australian Bureau of Statistics 1999, \textit{Disability, ageing and carers: summary of findings}, cat. no. 4430.0, & \fullcite{agsm54} & \texttt{agsm54} \\
	Dabrowski, W 1999, \textit{Caring for country}, report to the Aboriginal and Torres Strait Islander Commission, & \fullcite{agsm55} & \texttt{agsm55} \\
	Topp, L \& Dillon, P 1996, \textit{Looking to the future: a second generation of drug research}, monograph no. 29, & \fullcite{agsm47} & \texttt{agsm47} \\
\end{citetable}

\subsubsection{Edition}

\begin{citetable}
	Thompson, J \& O'Reilly, T 2000, \textit{Mammals of Australia}, 3rd edn, vol. 2, & \fullcite{agsm56} & \texttt{agsm56} \\
	Gowers, Sir Earnest 1983, \textit{The complete plain words}, 2nd edn, rev. Sir Bruce Fraser, & \fullcite{agsm57} & \texttt{agsm57} \\
	\textit{Roget's thesaurus of English words and phrases} 1987 (1852), & \majorissue{\fullcite{agsm58b}} & \texttt{agsm58b} \\
\end{citetable}

\subsubsection{Editor, compiler, reviser or translator}

\begin{citetable}
	Blundell, R 2000, \textit{Forest trees of south-western Tasmania}, ed. JB Kirkpatrick, & \fullcite{agsm59} & \texttt{agsm59} \\
	Kaunda, S (ed.) 1999, & \fullcite{agsm60} & \texttt{agsm60} \\
	Neyland, MG \& Duncan, F (comps) 1994, & \fullcite{agsm27} & \texttt{agsm27} \\
	Bryant, SL 1989, `Growth, development and breeding patterns of the long-nosed potoroo', in G Grigg, P Jarman \& I Hume (eds), \textit{Kangaroos, wallabies and rat kangaroos}, & \fullcite{agsm61} & \texttt{agsm61} \\
\end{citetable}

\subsubsection{Volume number or number of volumes}

\begin{citetable}
	Public Land Use Commission 1998, \textit{Tasmania--Commonwealth Regional Forest Agreement: environment and heritage report}, vol. 1, \textit{Background report}, & \fullcite{agsm62} & \texttt{agsm62} \\
	Public Land Use Commission 1999, \textit{Tasmania--Commonwealth Regional Forest Agreement: environment and heritage report}, vols 2 \& 3, & \minorissue{\fullcite{agsm63}} & \texttt{agsm63} \\
	Public Land Use Commission 2000, \textit{Tasmania--Commonwealth Regional Forest Agreement: environment and heritage report}, 4 vols, & \fullcite{agsm64} & \texttt{ags64} \\
\end{citetable}

\subsubsection{Publisher}

\begin{citetable}
	Begon, M, Harper, JL \& Townsend, CR 1988, \textit{Ecology: individuals, populations and communities}, Blackwell Scientific Publications, & \fullcite{agsm65} & \texttt{agsm65} \\
	Topp, L \& Dillon, P 1996, \textit{Looking to the future: a second generation of drug research}, monograph no. 29, National Drug and Alcohol Research Centre, & \fullcite{agsm47} & \texttt{agsm47} \\
	Australian Bureau of Statistics 2000, \textit{Australian social trends}, cat. no. 4102.0, ABS, & \fullcite{agsm66} & \texttt{agsm66} \\
	Egerton, MC 1996, \textit{The Australian film industry: an overview}, Dominion Press, Adelaide, \& Cinnamon Publishing, St Lucia, Qld. & \fullcite{agsm67} & \texttt{agsm67} \\
	Bligh, B 1980, \textit{Cherish the earth}, David Ell Press, Sydney, in assoc. with the National Trust of Australia (NSW), Sydney. & \fullcite{agsm68} & \texttt{agsm68} \\
\end{citetable}

\subsubsection{Place of publication}

\begin{citetable}
	Comfort, A 1997, \textit{A good age}, Mitchell Beazley, London. & \fullcite{agsm48} & \texttt{agsm48} \\
	Madden, R \& Hogan, T 1997, \textit{The definition of disability in Australia: moving towards national consistency}, Australian Institute of Health and Welfare, Canberra. & \fullcite{agsm69} & \texttt{agsm69} \\
	Raymond, R \& Watson-Munro, C 1990, \textit{The energy crisis of 1985}, Castle Books, n.p. Distributed in Australia by Horwitz-Grahame, Sydney. & \fullcite{agsm70} & \texttt{agsm70} \\
\end{citetable}

\subsubsection{Page number or numbers}

\begin{citetable}
	Comfort, A 1997, \textit{A good age}, Mitchell Beazley, London, pp.~31--59. & \fullcite{agsm48} & \texttt{agsm48} \\
\end{citetable}

\subsection{Journals}

\subsubsection{Title of article}

\begin{citetable}
	Doll, R 1997, `One for the heart', & \fullcite{agsm71} & \texttt{agsm71} \\
	Mercer, BB 2000, `Fantasy and ``King Lear''', & \fullcite{agsm72} & \texttt{agsm72} \\
	Nakajima, S 2001, `Aboard the ``Lusitania'' to Djibouti', & \fullcite{agsm73} & \texttt{agsm73} \\
	Lalumi\`{e}re, P 1995, `Note sur une exp\'{e}rience de financement priv\'{e} des investissements publiques' (Note on an experiment involving private financing of public investments) & \fullcite{agsm74} & \texttt{agsm74} \\
\end{citetable}

\subsubsection{Title of journal}

\begin{citetable}
	Doll, R 1997, `One for the heart', \textit{British Medical Journal}, & \fullcite{agsm71} & \texttt{agsm71} \\
	Lalumi\`{e}re, P 1995, `Note sur une exp\'{e}rience de financement priv\'{e} des investissements publiques' (Note on an experiment involving private financing of public investments), \textit{Revue de science financi\`{e}re}, & \fullcite{agsm74} & \texttt{agsm74} \\
\end{citetable}

\subsubsection{Title of series}

\begin{citetable}
	Pilli, L 1999, `The life of George Bernard Shaw', \textit{Bibliographical Essays}, British history series, & \fullcite{agsm75} & \texttt{agsm75} \\
\end{citetable}

\subsubsection{Issue details and page reference}

\begin{citetable}
	Doll, R 1997, `One for the heart', \textit{British Medical Journal}, vol.~315, pp.~20--7. & \fullcite{agsm71} & \texttt{agsm71} \\
	Gershuny, J 1996, `Time use, technology and the future of work', \textit{Journal of the Market Research Society}, vol.~28, no.~4, pp.~335--9. & \fullcite{agsm76} & \texttt{agsm76} \\
	Dewhirst, C 1996, `Hot air over the Himalays', \textit{World Geographic}, vol.~1, October--December, pp.~51--61. & \fullcite{agsm77} & \texttt{agsm77} \\
	Bell, J 1996, `Flying high in the Andes', \textit{World Geographic} (Sydney), vol.~79, no.~4, pp.~19--25. & \fullcite{agsm78} & \texttt{agsm78} \\
	Cronin, AP 1993, `The Scottish coastline: waves at work', \textit{World Geographer} (London), vol.~17, autumn, pp.~11--21. & \fullcite{agsm79} & \texttt{agsm79} \\
	Wood, C 1998, `Cocaine's chaos', \textit{Connexions}, August--September, Centre for Education and Information on Drugs and Alcohol, Sydney, pp.~11--13. & \fullcite{agsm79x} & \texttt{agsm79x} \\
\end{citetable}

\subsection{Other Periodicals}

\begin{citetable}
	Brent, BB 2000, `Taking the next step', \textit{Quarterly Review}, vol.~199, no.~9, pp.~33--9. & \fullcite{agsm80} & \texttt{agsm80} \\
	Cowley, T 2001, `One people, one destiny', \textit{Australian Geographic}, vol~ 61, January--March, pp. 48--67. & \fullcite{agsm81} & \texttt{agsm81} \\
	Michaelis, PL 1999, `Farming trends in perspective', \textit{Bingara Observer}, 22 December, p.~21. & \fullcite{agsm82} & \texttt{agsm82} \\
\end{citetable}

\subsubsection{Magazines}

\begin{citetable}
	Light, D 2000, `A tax on the jitters', \textit{Bulletin}, 18 January, pp.~50--1. & \fullcite{agsm83} & \texttt{agsm83} \\
	Treloar, B 1999, `Grains of sense', \textit{Australian Gormet Traveller}, November, pp.~29--30, 64. & \fullcite{agsm84} & \texttt{agsm84} \\
\end{citetable}

\subsubsection{Newspapers}

\begin{citetable}
	Towers, K 2000, `Doctor not at fault: coroner', \textit{Australian}, 18 January, p.~3. & \fullcite{agsm85} & \texttt{agsm85} \\
	(\textit{Sydney Morning Herald} 24 January 2000, p.~12) & \majorissue{\parencite{agsm86}} & \texttt{agsm86} \\
	\textellipsis{} in the \textit{Sydney Morning Herald} (24 January 2000, p.~12) & \textellipsis{} in the \majorissue{\textcite{agsm86}} & \texttt{agsm86} \\
	(\textit{Financial Review} 18 January 2000, editorial) & \majorissue{\parencite{agsm87}} & \texttt{agsm87} \\
\end{citetable}

\subsubsection{Reviews in periodicals}

\begin{citetable}
	Riemer, A 2000, `Australian gothic revisited', review of \textit{Prelude to Christopher} by Eleanor Dark, \textit{Sydney Morning Herald}, 22 January, p.~12s. & \majorissue{\fullcite{agsm88}} & \texttt{agsm88} \\
\end{citetable}

\subsection{Media Releases}

\begin{citetable}
	Watersmith, C 2000, \textit{BHP enters new era}, media release, BHP Limited, Melbourne, 1 March. & \fullcite{agsm89} & \texttt{agsm89} \\
	Smith, A (Minister for Justice and Customs) 1999, \textit{Coastwatch initiative bears fruit}, media release, Parliament House, Canberra, 21 July. & \fullcite{agsm90} & \texttt{agsm90} \\
\end{citetable}

\subsection{Published proceedings}

\begin{citetable}
	Bourassa, S 1999, `Effects of child care on young children', \textit{Proceedings of the third annual meeting of the International Society for Child Psychology}, International Society for Child Psychology, Atlanta, Georgia, pp.~44--6. & \fullcite{agsm91} & \texttt{agsm91} \\
\end{citetable}

\subsection{Unpublished material}

\begin{citetable}
	Herber, KA 1995, `Parallel knowledge: farmers and scientists and land classification', BAppSc thesis, University of Canberra. & \fullcite{agsm92} & \texttt{agsm92} \\
	Bowden, FJ \& Fairley, CK 1996, `Endemic STDs in the Northern Territory: estimations of effective rates of partner change', paper presented to the scientific meeting of the Royal Australian College of Physicians, Darwin, 24--25 June. & \fullcite{agsm93} & \texttt{agsm93} \\
	Corey, L 1997, `The clinical implications of interactions between HIV and HSV', abstract presented at the 5th annual meeting of the International Herpes Management Forum, Cannes, France, 12--15 August. & \fullcite{agsm94} & \texttt{agsm94} \\
	Adams, DE 1917, `My journey to Khartoum', in possession of MA Adams, Adelaide. & \fullcite{agsm95} & \texttt{agsm95} \\
	Ecclestone, A 1934, `A year in the wilderness', in possession of the Mitchell Library, Sydney. & \fullcite{agsm96} & \texttt{agsm96} \\
	Hudson, DE 1909--18, `Diary', Hudson Papers, Fisher Library, University of Sydney. & \trivialissue{\fullcite{agsm97}} & \texttt{agsm97} \\
	Thompson, BE 1987, `Recollections of the Raj', in possession of the author, Melbourne. & \fullcite{agsm98} & \texttt{agsm98} \\
\end{citetable}

\section{Specialised sources}

\subsection{Legislation}

\subsubsection{Acts and ordinances}

\begin{citetable}
	the \textit{Environment Protection (Impact of Proposals) Act 1974} \textellipsis{} the Environment Protection (Impact of Proposals) Act \textellipsis{} & & \texttt{agsm99} \\
	the \textit{Casino Control Ordinance 1988} \textellipsis{} the Casino Control Ordinance & & \texttt{agsm100} \\
	The Commonwealth's \textit{A New Tax System (Wine Equalisation Tax) Act 1999} mask provision for & & \texttt{agsm101} \\
	Victoria's \textit{Equal Opportunity Act 1995} prohibits & & \texttt{agsm102} \\
	In Victoria the \textit{Equal Opportunity Act 1995} prohibits & & \texttt{agsm102} \\
	The Christmas Island \textit{Casino Control Ordinance 1988} makes provision for & & \texttt{agsm100} \\
	the \textit{Copyright Act 1968} (Cwlth) & & \texttt{agsm103} \\
	the \textit{Anti-Discrimination Act 1991} (Qld) & & \texttt{agsm104} \\
	the \textit{Equal Opportunity Act 1984} (WA) & & \texttt{agsm105} \\
	The Sale of Foods Act 2000 (UK) & & \texttt{agsm106} \\
\end{citetable}

\subsubsection{Regulations and other forms of delegated legislation}

\begin{citetable}
	the Customs (Prohibited Imports) Regulations & & \texttt{agsm107} \\
\end{citetable}

\subsubsection{Units of division}

\begin{citetable}
	Section 4 of the Commonwealth's \textit{Copyright Act 1968} & & \texttt{agsm103} \\
	In ss.~4--7 of the \textit{Copyright Act 1968} (Cwlth) & & \texttt{agsm103} \\
	The \textit{Copyright Act 1968}, s.~4, \textellipsis{} & & \texttt{agsm103} \\
	Section 4 of the \textit{Casino Control Ordinance 1988} & & \texttt{agsm100} \\
	The Commonwealth's Copyright Regulations, r.~18, \textellipsis{} & & \texttt{agsm108} \\
	The Copyright Regulations, rr.~18--19, \textellipsis{} & & \texttt{agsm108} \\
	Regulation 18 of the Copyright Regulations (Cwlth) & & \texttt{agsm108} \\
	In r.~4 of the Copyright Regulations & & \texttt{agsm108} \\
	In rr.~18--19 of the Copyright Regulations & & \texttt{agsm108} \\
	the Commonwealth's \textit{Airlines Equipment Amendment Act 1981}, s.~19(1)(a)(ii) & & \texttt{agsm109} \\
	the Public Service Regulations (Cwlth), r.~83(2)(a)(ii) & & \texttt{agsm110} \\
	In Part IV of the \textit{Copyright Act 1968} & & \texttt{agsm103} \\
\end{citetable}

\subsubsection{Bills}

\begin{citetable}
	the Regulation of Genetic Material Bill 2000 & & \texttt{agsm111} \\
\end{citetable}

\subsection{Legal authorities}

\subsubsection{The name of the case}

\begin{citetable}
	\textit{The State of New South Wales v.~The Commonwealth} (1915) 20 CLR 54 & & \texttt{agsm112} \\
	\textit{Greutner v.~Everard} (1960) 103 CLR 177 at 181 & & \texttt{agsm113} \\
	\textit{Jamieson v.~Cooper} (1942) 67 CLR 316 & & \texttt{agsm114} \\
	\textit{Clark King \& Co.~Pty Ltd v.~Australian Wheat Board} (1978) 140 CLR 120 & & \texttt{agsm115} \\
	\textit{re Smith} & & \texttt{agsm116} \\
	\textit{re Smith \& ors} & & \texttt{agsm117} \\
	\textit{ex parte Smith \& anor} & & \texttt{agsm118} \\
	\textit{R v.~Haddock} & & \texttt{agsm119} \\
	\textit{Haddock v.~The Queen} & & \texttt{agsm120} \\
	\textit{The State of New South Wales v.~The Commonwealth} (1915) 20 CLR 54 (the \textit{Wheat Case}) & & \texttt{agsm121} \\
	That was the opinion of Latham CJ and McTiernan J in \textit{Attorney-General (Vic.) v.~The Commonwealth} (1946) 71 CLR 237 at 253--6 and 273--4.  A somewhat more restricted view was taken by Starke J (at 266), Dixon and Rich JJ (at 271--2), and Williams J (at 281--3). & & \texttt{agsm122} \\
\end{citetable}

\subsubsection{Reference details}

\begin{citetable}
	In \textit{Commonwealth v.~ Anderson} (1960) 105 CLR 303; (1960) 34 ALJR 323 & & \texttt{agsm123} \\
\end{citetable}

\subsection{Plays and poetry}

\begin{citetable}
	William Shakespeare, \textit{Romeo and Juliet}, act 3, scene 2, line 74 & & \texttt{agsm124} \\
	Judith Wright, \textit{Woman to child}, verse 1, lines 3--4 & & \texttt{agsm125} \\
\end{citetable}

\subsection{The classics}

\begin{citetable}
	Virgil, \textit{Eclogues}, `The dispossessed', line 70, trans. EV Rieu, Penguin, Harmondsworth, UK, 1967. & & \texttt{agsm126} \\
\end{citetable}

\subsection{Films, videos, and television and radio programs}

\begin{citetable}
	\textit{Strictly ballroom} (1992) & & \texttt{agsm127} \\
	(\textit{Understanding the GNP} 1982) & & \texttt{agsm128} \\
	\textit{Grumpy meets the orchestra} 1992, video recording, Australian Broadcasting Corporation, Sydney. Featuring the Sydney Symphony Orchestra. & & \texttt{agsm129} \\
	\textit{Sunday too far away} 1975, motion picture, South Australian Film Corporation, Adelaide. Distributed by Rainbow Products Ltd, Sydney, and starring Jack Thompson, Reg Lye and Max Cullen. & & \texttt{agsm130} \\
	\textit{What are we going to do with the money?} 1997, television program, SBS TElevision, Sydney, 8 August. & & \texttt{agsm131} \\
\end{citetable}

\subsection{Duplicated material}

\begin{citetable}
	Huntingdon, EWB 1997, \textit{Economies in the Australian beef industry}, microfiche, Australian Livestock Council, Canberra. & & \texttt{agsm132} \\
	Moss, C 1999, \textit{The Australian merino: a brief summary of recent developments}, photocopy, Department of Agriculture, Sydney, 1999. & & \texttt{agsm133} \\
\end{citetable}

\subsection{Databases}

\begin{citetable}
	AGRIS database, United Nations Food and Agriculture Organization, SilverPlatter (vendor), annual updating. & & \texttt{agsm134} \\
\end{citetable}

\section{Electronic material}

\subsection{Web site}

\begin{citetable}
	Department of Finance and Administration 2001, Department of Finance and Administration, Canberra, viewed 7 August 2001, \citeurlex{http://www.finance.gov.au}. & \fullcite{agsm135} & \texttt{agsm135} \\
	International Narcotics Control Board 1999, United Nations, Vienna, viewed 1 October 1999, \citeurlex{http://www.incb.org}. & \fullcite{agsm136} & \texttt{agsm136} \\
	Details of the program are available from the department's web site \citeurlex{http://www.finance.gov.au} & Details of the program are available form the department's web site \citeurl{agsm135} & \texttt{agsm135} \\
	The International Narcotics Control Board's web site \citeurlex{http://www.incb.org} provides details of the program & The International Narcotics Control Board's web site \citeurl{agsm136} provides details of the program & \texttt{agsm136} \\
\end{citetable}

\subsection{Document within a web site}

\begin{citetable}
	Anderson, J (Minister for Transport and Regional Services) 2000, \textit{CASA approves avgas contamination test}, media release, 23 January, Department of Transport and Regional Services, Canberra, viewed 7 February 2000, \citeurlex{http://www.dotrs.gov.au/media/anders/archive/2000/jan\textunderscore 00/al6\textunderscore 2000.htm}. & \minorissue{\fullcite{agsm137}} & \texttt{agsm137} \\
	Attorney-General's Department 1998, \textit{Review of the Commonwealth `Acts Interpretation Act 1901'}, Attorney-General's Department, Canberra, viewed 5 April 2001, \citeurlex{http://www.law.gov.au}. & \fullcite{agsm138} & \texttt{agsm138} \\
	International Narcotics Control Board 1998, \textit{International Narcotics Control Board report for 1998}, United Nations, Vienna, viewed 1 October 1999, \citeurlex{http://www.incb.org/e/index.htm}. & \fullcite{agsm139} & \texttt{agsm139} \\
\end{citetable}

\subsection{Electronic mail lists, Usenet groups and bulletin boards}

\begin{citetable}
	Murphy, L \textless{}murphy@rockets.com.au\textgreater{} 2000, `News for old hacks', list server, 20 January, National Journalists Association, viewed 7 February, \citeurlex{http://www.nja.net.au/listserv/}. & \minorissue{\fullcite{agsm140}} & \texttt{agsm140} \\
\end{citetable}

\subsection{CD-ROMs}

\begin{citetable}
	(\textit{Dr Brain thinking games} 1998) & \parencite{agsm141} & \texttt{agsm141} \\
	\textit{Dr Brain thinking games} (1998) & \textcite{agsm141} & \texttt{agsm141} \\
	\textit{Dr Brain thinking games} 1998, CD-ROM, Knowledge Adventure Inc., Torrance, California. & \fullcite{agsm141} & \texttt{agsm141} \\
\end{citetable}

\printbibliography

\clearpage
\part{University of New South Wales}
\fullcite{unsw}
\newrefsection

\section{Citing different sources}

\subsection{Books}

\begin{citetable}
	(Karskens 1997, p. 23) & \parencite[p.~23]{unsw1} & \texttt{unsw1} \\
	Ward (1966, p. 12) suggests that & \textcite[p.~12]{unsw2} suggests that & \texttt{unsw2} \\
	Karskens, G 1997, \textit{The Rocks: life in early Sydney}, Melbourne University Press, Carlton. & \fullcite{unsw1} & \texttt{unsw1} \\
	Ward, R 1966, \textit{The Australian legend}, 2nd edn, Oxford University Press, Melbourne. & \fullcite{unsw2} & \texttt{unsw2} \\
\end{citetable}

\subsection{Edited book collections}

\subsubsection{A chapter from a book collection}

\begin{citetable}
	(Curthoys 1997, p. 25) & \parencite[p.~25]{unsw3} & \texttt{unsw3} \\
	Curthoys, A 1997, `History and identity', in W Hudson \& G Bolton (eds), \textit{Creating Australia: changing Australian history}, Allen \& Unwin, Sydney, pp. 23-38 & \fullcite{unsw3} & \texttt{unsw3} \\
\end{citetable}

\subsubsection{An entire book collection}

\begin{citetable}
	(Hudson \& Bolton 1997) & \parencite{unsw4} & \texttt{unsw4} \\
	Hudson, W \& Bolton, G (eds) 1997, \textit{Creating Australia: changing Australian history}, Allen \& Unwin, Sydney. & \fullcite{unsw4} & \texttt{unsw4} \\
\end{citetable}

\subsection{Journal articles}

\begin{citetable}
	(Kozulin 1993, p.~257) & \parencite[p.~257]{unsw5} & \texttt{unsw5} \\
	(Kozulin 1993) & \parencite{unsw5} & \texttt{unsw5} \\
	Kozulin, A 1993, `Literature as a psychological tool', \textit{Educational Psychologist}, vol.~28, no.~3, pp.~253-65, DOI:10.1207/s15326985ep2803\_5. & \minorissue{\fullcite{unsw5}} & \texttt{unsw5} \\
\end{citetable}

\subsection{Newspapers and magazines}

\begin{citetable}
	(\textit{Sydney Morning Herald} 7 March, 1994, p.~8) & \majorissue{\parencite{unsw6}} & \texttt{unsw6} \\
	`UNSW gains top ranking from quality team' 1994, \textit{Sydney Morning Herald}, 28 February, p.~21. & \fullcite{unsw7} & \texttt{unsw7} \\
	(Donaghy 1994, p.~3) & \parencite[p.~3]{unsw8} & \texttt{unsw8} \\
	Donaghy, B 1994, `National meeting set to review tertiary admissions', \textit{Campus News}, 3--9 March, p.~3. & \fullcite{unsw8} & \texttt{unsw8} \\
\end{citetable}

\subsection{Government publications}

\begin{citetable}
	(Department of Education, Science \& Training 2000) & \parencite{unsw9} & \texttt{unsw9} \\
	Department of Education, Science \& Training 2000, \textit{Annual Report 1999-2000}, AGPS, Canberra. & \fullcite{unsw9} & \texttt{unsw9} \\
\end{citetable}

\subsection{Unpublished material}

\begin{citetable}
	(Ballard 2003, p. 132) & \parencite[p.~132]{unsw10} & \texttt{unsw} \\
	Ballard, BA 2003, `The seeing machine: photography and the visualisation of culture in Australia, 1890-1930', PhD thesis, University of Melbourne. & \fullcite{unsw10} & \texttt{unsw10} \\
	(Fitzsimmons 2005) & \parencite{unsw11} & \texttt{unsw11} \\
	Fitzsimmons, D 2005, `Who chooses who belongs: tactics and strategies and migrant literature', paper presented at the AULLA \& FILLM conference, James Cook University, Cairns, 15-19 July. & \fullcite{unsw11} & \texttt{unsw11} \\
\end{citetable}

\subsection{ABS statistics}

\begin{citetable}
	(Australian Bureau of Statistics 2005) & \majorissue{\parencite{unsw12}} & \texttt{unsw12} \\
	(ABS 2006) & \parencite{unsw13} & \texttt{unsw13} \\
	Australian Bureau of Statistics 2005, \textit{New South Wales in focus}, cat.~no.~1338.1, Australian Bureau of Statistics, Canberra. & \fullcite{unsw12} & \texttt{unsw12} \\
	Australian Bureau of Statistics 2007, \textit{Internet Activity, Australia}, Sep 2006, cat.~no.~8153.0, Australian Bureau of Statistics, Canberra, accessed 11 April 2007, \citeurlex{http://www.abs.gov.au}. & \fullcite{unsw14} & \texttt{unsw14} \\
\end{citetable}

\subsection{Brochure}

\begin{citetable}
	(New South Wales Dept of Primary Industries 2005) & \parencite{unsw15} & \texttt{unsw15} \\
	New South Wales Dept of Primary Industries 2005, \textit{Saltwater recreational fishing in New South Wales: rules \& regulations summary}, brochure, NSWDPI, New South Wales. & \fullcite{unsw15} & \texttt{unsw15} \\
\end{citetable}

\section{How to cite references}

\subsection{An author who attributes information to another source}

\begin{citetable}
	Graham Gibbs, in his 1981 study into student learning wrote that ``because students are aware of their tutor's mastery of the subject matter, it is quite common for them to assume that their reader has no needs at al'' (Gibbs 1981, p. 39, cited in Bowden \& Marton 1998, p. 35). & Graham Gibbs, in his 1981 study into student learning wrote that ``because students are aware of their tutor's mastery of the subject matter, it is quite common for them to assume that their reader has no needs at all'' \mkbibparens{Gibbs 1981, p.~39, cited in \cite[p.~35]{unsw35}} & \texttt{unsw35} \\
	Bowden, J \& Marton F 1998, \textit{The university of learning}, Kogan Page, London. & \fullcite{unsw35} & \texttt{unsw35} \\
\end{citetable}

\subsection{More than one author}

\begin{citetable}
	(Gerster \& Basset 1991) & \parencite{unsw36} & \texttt{unsw36} \\
	Gerster and Basset (1991) assert that & \textcite{unsw36} assert that & \texttt{unsw36} \\
	Gerster, R \& Basset, J 1991, \textit{Seizures of youth: the sixties and Australia}, Hyland House, Melbourne. & \fullcite{unsw36} & \texttt{unsw36} \\
	Leeder et all. (1996, p. 78) argued & \textcite[p.~78]{unsw37} argued & \texttt{unsw37} \\
	(Leeder et al. 1996) & \parencite{unsw37} & \texttt{unsw37} \\
	Leeder, SR, Dobson, AJ, Gibbers, RW, Patel, NK, Matthews, PS, Williams DW \& Mariot, DL 1996, \textit{The Australian film industry}, Dominion Press, Adelaide. & See the bibliography. & \texttt{unsw37} \\
\end{citetable}

\subsection{A work reproduced in a book (image, poem, painting etc)}

\begin{citetable}
	De Kooning's 1952 painting ``Woman and Bicycle'' (Hughes 1980, p. 295) is an example of & De Kooning's 1952 painting ``Woman and Bicycle'' \parencite[p.295]{unsw38} is an example of & \texttt{unsw38} \\
	Hughes, R 1980, \textit{The shock of the new: art and the century of change}, British Broadcasting Corporation, London. & \fullcite{unsw38} & \texttt{unsw38} \\
\end{citetable}

\subsection{More than one work by the same author}

\begin{citetable}
	(Smith 1981, 1984, 1985) & \parencite{unsw39,unsw40,unsw41} & \texttt{unsw39} \texttt{unsw40} \texttt{unsw41} \\
\end{citetable}

\subsection{Part of a publication contributed by a someone other than the main author}

\begin{citetable}
	Drabble (in Bronte 1978) suggests & Drabble (in \cite{unsw42}) suggests & \texttt{unsw42} \\
	Bronte, E 1978, \textit{Wuthering Heights and poems}, H Osborne (ed.), Orion Publishing Group, London. Introduction by Margaret Drabble. & \minorissue{\fullcite{unsw42}} & \texttt{unsw42} \\
\end{citetable}

\subsection{An author who published more than one work in the same year}

\begin{citetable}
	Dawkins (1972a, 1972b) completed a number of studies on & \textcite{unsw43,unsw44} completed a number of studies on & \texttt{unsw43} \texttt{unsw44} \\
\end{citetable}

\subsection{To refer to more than one work in an in-text citation}

\begin{citetable}
	(Entwistle 1977; Haddon 1969) & \parencite{unsw45,unsw46} & \texttt{unsw45} \texttt{unsw46} \\
	Entwistle (1977) and Haddon (1969) both demonstrated & \textcite{unsw45} and \textcite{unsw46} both demonstrated & \texttt{unsw45} \texttt{unsw46} \\
\end{citetable}

\subsection{Authors with the same family name who have published in the same year}

\begin{citetable}
	The theory was first developed early this century (Smyth, AK 1979) but later many of its elements were refuted (Smyth, JA 1979). & The theory was first developed early this century \parencite{unsw47} but later many of its elements were refuted \parencite{unsw48}. & \texttt{unsw47} \texttt{unsw48} \\
\end{citetable}

\section{How to cite electronic sources}

\subsection{Websites}

\begin{citetable}
	(International Narcotics Control Board 1999) & \parencite{unsw16} & \texttt{unsw16} \\
	International Narcotics Control Board 1999, United Nations, accessed 1 October 1999, \citeurlex{http://www.incb.org} & \fullcite{unsw16} & \texttt{unsw16} \\
\end{citetable}

\subsubsection{A page or document within a website}

\begin{citetable}
	(Winston 1999) & \parencite{unsw17} & \texttt{unsw17} \\
	Winston, J 1999, \textit{A look at referencing}, AAA Educational Services, accessed 20 October 2002, \citeurlex{http://www.aaa.edu.au/aaa.html}. & \fullcite{unsw17} & \texttt{unsw17} \\
	(World Health Organisation 2013) & \parencite{unsw18} & \texttt{unsw18} \\
	World Health Organisation 2013, \textit{Financial crisis and global health}, United Nations, accessed 1 August 2013, \citeurlex{http://www.who.int/topics/financial\_crisis/en/}. & \fullcite{unsw18} & \texttt{unsw18} \\
\end{citetable}

\subsubsection{No author}

\begin{citetable}
	(\textit{Land for sale on moon} 2007) & \parencite{unsw19} & \texttt{unsw19} \\
	\textit{Land for sale on moon} 2007, accessed 19 June 2007, \citeurlex{http://www.moonlandregistry.com}. & \fullcite{unsw19} & \texttt{unsw19} \\
\end{citetable}

\subsubsection{No date}

\begin{citetable}
	(ArtsNSW n.d.) & \parencite{unsw20} & \texttt{unsw20} \\
	ArtsNSW n.d., \textit{New South Wales Premier’s Literary Awards}, NSW Department of the Arts, Sport and Recreation, accessed 19 June 2007, \citeurlex{http://www.arts.nsw.gov.au/awards/LiteraryAwards/litawards.htm}. & \fullcite{unsw20} & \texttt{unsw20} \\
\end{citetable}

\subsection{Online journals}

\begin{citetable}
	(Morris 2004, sec. 3, par. 2) & \parencite[sec.~3,~par.~2]{unsw21} & \texttt{unsw21} \\
	Morris, A 2004, `Is this racism? Representations of South Africa in the Sydney Morning Herald since the inauguration of Thabo Mbeki as president', \textit{Australian Humanities Review}, no. 33, accessed 11 May 2007, \citeurlex{http://www.australianhumanitiesreview.org/archive/Issue-August-2004/morris.html}. & \fullcite{unsw21} & \texttt{unsw21} \\
	Rowland, TA 2015, `Feminism from the Perspective of Catholicism', \textit{Solidarity: The Journal of Catholic Social Thought and Secular Ethics}, vol. 5, no. 1, accessed 12 December 2015, \citeurlex{http://researchonline.nd.edu.au/solidarity/vol5/iss1/1}. & \fullcite{unsw22} & \texttt{unsw22} \\
\end{citetable}

\subsection{E-Books}

\begin{citetable}
	Lloyd (2005, p. 262) & \textcite[p.~262]{unsw23} & \texttt{unsw23} \\
	(Lloyd 2005, p. 262) & \parencite[p.~262]{unsw23} & \texttt{unsw23} \\
\end{citetable}

\subsubsection{Accessed online}

\begin{citetable}
	Lloyd, CB (ed.) 2005, \textit{Growing up global: The changing transitions for adulthood in developing countries}, e-book, accessed 5 May 2007, \citeurlex{http://www.nap.edu/books/11174/html/index.html}. & \fullcite{unsw23} & \texttt{unsw23} \\
\end{citetable}

\subsubsection{Accessed via a database}

\begin{citetable}
	Woodham, JM 2004, \textit{A dictionary of modern design}, e-book, accessed 25 July 2007 from Oxford Reference Online Database. & \majorissue{\fullcite{unsw24}} & \texttt{unsw24} \\
\end{citetable}

\subsubsection{Accessed via an e-book reader}

\begin{citetable}
	(Smith 2008) & \parencite{unsw25} & \texttt{unsw25} \\
	Smith (2008) states that & \textcite{unsw25} states that & \texttt{unsw25} \\
	Smith, A 2008, \textit{The Wealth of Nations}, Kindle version, accessed 20 August 2010 from Amazon.com. & \fullcite{unsw25} & \texttt{unsw25} \\
	Smith, A 2009, \textit{The Wealth of Nations}, Adobe Digital Editions version, accessed 20 August 2010, doi: 10.1036/007142363X. & \majorissue{\fullcite{unsw26}} & \texttt{unsw26} \\
\end{citetable}

\subsection{Database items}

\subsubsection{A journal article accessed from a full-text database}

\begin{citetable}
	(Nicholls 2006, p. 171) & \parencite[p.~171]{unsw27} & \texttt{unsw27} \\
	Nicholls, D 2006, ``Does the meaning mean a thing?': Johnny Young's hit songs of the 60s-70s', \textit{Australian Cultural History}, No 2, pp. 163-183, accessed 11 May 2007 from Informit Full Text Database, ISSN; 0728-8433. & \majorissue{\fullcite{unsw27}} & \texttt{unsw27} \\
	(Holmes 2004) & \parencite{unsw28} & \texttt{unsw28} \\
	Holmes, S 2004, ``But this Time You Choose!': Approaching the `Interactive' audience in reality TV', \textit{International Journal of Cultural Studies}, No. 7, pp. 213-231, accessed 3 March 2007 from Sage Journals Online. & \majorissue{\fullcite{unsw28}} & \texttt{unsw28} \\
\end{citetable}

\subsubsection{A thesis accessed from a database} 

\begin{citetable}
	(Lee 2005, p. 78) & \parencite[p.~78]{unsw29} & \texttt{unsw29} \\
	Lee, C 2005, `Beyond the Pink: (Post) Youth Iconography in Cinema', PhD thesis, Murdoch University, accessed 15 June 2007 from Australian Digital Thesis Program Database. & \majorissue{\fullcite{unsw29}} & \texttt{unsw29} \\
\end{citetable}

\subsection{Online newspapers}

\subsubsection{Accessed from a full-text database}

\begin{citetable}
	(Pianin 2001) & \parencite{unsw30} & \texttt{unsw30} \\
	Pianin, E 2001, `As coal's fortunes climb, mountains tremble in W.Va; energy policy is transforming lives', \textit{The Washington Post}, 25 February, p. A03, accessed March 2001 from Electric Library Australasia. & \majorissue{\fullcite{unsw30}} & \texttt{unsw30} \\
\end{citetable}

\subsubsection{Without a named author} 

\begin{citetable}
	(\textit{New York Daily Times} 1851) & \majorissue{\parencite{unsw31}} & \texttt{unsw31} \\
	`Amending the Constitution', \textit{New York Daily Times}, 16 October 1851, p. 2, accessed 15 July 2007 from ProQuest Historical Newspapers database. & \majorissue{\fullcite{unsw31}} & \texttt{unsw31} \\
	An account of the popularity of the baby tapir in \textit{The Independent} (2013) stated that & An account of the popularity of the baby tapir in \majorissue{\textcite{unsw32}} stated that & \texttt{unsw32} \\
	`Baby tapir wins hearts at zoo', \textit{The Independent}, 9 August 2013, Accessed 25 January 2014, \citeurlex{http://www.independent.ie/world-news/and-finally/baby-tapir-wins-hearts-at-zoo-30495570.html}. & \fullcite{unsw32} & \texttt{unsw32} \\
\end{citetable}

\subsubsection{Online article} 

\begin{citetable}
	(Coorey 2007) & \parencite{unsw33} & \texttt{unsw33} \\
	Coorey, P 2007, `Costello hints at green safety net', \textit{Sydney Morning Herald}, 10 May, accessed 14 May 2012, \citeurlex{http://www.smh.com.au/news/business/costello-hints-at-green-safety-net/2007/05/09/1178390393875.html} & \fullcite{unsw33} & \texttt{unsw33} \\
\end{citetable}

\subsection{Media releases}

\begin{citetable}
	Prime Minister Howard (2007) announced plans for further welfare reform & Prime Minister Howard \mkbibparens{\citeyear{unsw34}} announced plans for further welfare reform & \texttt{unsw34} \\
	Office of the Prime Minister 2007, \textit{Welfare Payments Reform}, media release, accessed 25 July 2007, \citeurlex{http://www.pm.gov.au/media/Release/2007/Media\_Release24432.cfm}. & \majorissue{\fullcite{unsw34}} & \texttt{unsw34} \\
\end{citetable}

\section{Broadcast materials and other electronic sources}

\subsection{Films, television and online videos}

\begin{citetable}
\end{citetable}

\subsection{Audio CD or CD ROM}

\begin{citetable}
\end{citetable}

\subsection{Blogs and wikis}

\begin{citetable}
\end{citetable}

\subsection{Emails and online communications}

\begin{citetable}
\end{citetable}

\subsection{Podcasts}

\begin{citetable}
\end{citetable}

\subsection{Twitter}

\begin{citetable}
\end{citetable}

\subsection{Facebook post}

\begin{citetable}
\end{citetable}

\section{Images and tables found online}

\begin{citetable}
\end{citetable}

\printbibliography
	
\end{document}